---
title: "binomial"
author: Ann Deng
date: May 3, 2019
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

`"binomial"` is a package that provides functions to summarize and visualize binomial distributions.

* `bin_variable()` creates a binvar object (of class `"binvar"`)
* `print.binvar()` method for a `"binvar"` object to print content
* `summary()` and `print.summary()` method for a `"binvar"` object

* `bin_mean()`, `bin_variance()`, `bin_mode()`, `bin_skewness()`, and `bin_kurtosis()` to calculate summary measures for given trials and probability

* `bin_choose()` calculates number of combinations in which *k* successes can occur in *n* trials
* `bin_probability()` calculates probability of obtaining given number of successes in trials
* `bin_distribution()` creates an object of both `"bindis"` and `"data.frame"` classes that tabulates the probability of obtaining given number of successes in trials
* `plot()` method for a `"bindis"` object to plot barchart of probabilities
* `bin_cumulative()` creates an object of both `"bincum"` and `"data.frame"` classes that tabulates cumulative probability of obtaining given number of successes in trials
* `plot()` method for a `"bincum"` object to plot cumulative probability


## Motivation

This package has been developed for Stat133, Sp2019 as an exercise in making packages.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r}
# development version from GitHub:
#install.packages("devtools") 
# install "cointoss" (without vignettes)
devtools::install_github("anndeng/binomial")
# install "cointoss" (with vignettes)
devtools::install_github("anndeng/binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)
# make binomial random variable object
binvar1 <- bin_variable(5, 0.5)
# mode of binvar with 10 trials, 0.5 prob of success
bin_mode(10, 0.5)
# combinations of 2 successes in 5 trials
bin_choose(5, 2)
# probability of 2 successes in 5 trials, 0.5 prob of success
bin_probability(2, 5, 0.5)
# probability distribution of 5 trials, 0.5 prob of success
bin_distribution(5, 0.5)
# cumulative probability of 5 trials, 0.5 prob of success
bin_cumulative(5, 0.5)
```
