---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## Binomial distributions

`"binomial"` is a simple package that provides functions to summarize and visualize binomial distributions.


## Summary measures

The functions `bin_mean()`, `bin_variance()`, `bin_mode()`, `bin_skewness()`, and `bin_kurtosis()` calculate summary measures for given values of trials and probability of success: 

```{r}
# 10 trials, 0.3 probability of success
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```

The arguments `trials` and `prob` must be non-negative, and `prob` must be between 0 and 1, inclusive. 


## binvar object

The function `bin_variable()` creates a `"binvar"` object:

```{r}
# 5 trials, 0.5 probability of success
binvar1 <- bin_variable(5, 0.5)
```

The function `summary()` may be used with a `"binvar"` object to display summary measures for the object. 


## bin_choose


The function `bin_choose()` calculates the number of combinations in which *k* successes can occur in *n* trials:

```{r}
# 2 successes in 5 trials
bin_choose(5, 2)
```


## bin_probability

The function `bin_probability()` outputs the given probability of obtaining a given number of successes in a number of trials:

```{r}
# 2 successes in 5 trials, 0.5 prob of success
binprob1 <- bin_probability(2, 5, 0.5)
binprob1
```


## bindis and bincum objects

The functions `bin_distribution()` and `bin_cumulative()` output a `"data.frame"` object containing the probabilities of obtaining all possible numbers of successes in a number of trials, and are invoked in the same manner as `bin_probability()`. These `"data.frame"` objects also have classes of `"bindis"` and `"bincum"`, respectively. 

The function `plot()` may be used to create graphics for both `"bindis"` and `"bincum"` objects.

```{r}
# 2 successes in 5 trials, 0.5 prob of success
bindis1 <- bin_distribution(5, 0.5)
plot(bindis1)

bincum1 <- bin_cumulative(5, 0.5)
plot(bincum1)
```

